### 2024-01-06 inst/doc/generalExploration.Rmd
move things out of vignetts and data

a=initAdaptiveTraits(ki=ki,km=km)
z=4 #number of neutral traits
neutraltraitsParam=initNeutralTraits(z = z)
neutraltraitsParam$s=c(0,0,1,1)

@@

tentries=replicate(10,modelOOstyle( N=N, Th=Th, K =K, m=m, b=b, r=r, rho=rho, d=d, maturity=maturity, endrepro=endrepro, logging="time", population=population, initcomus=initcomus, tstep=tstep, neutraltraitsParam=neutraltraitsParam))

>>>>

a=initAdaptiveTraits(ki=ki,km=km)
z=4 #number of neutral traits
neutraltraitsParam=initNeutralTraitsPathways(z = z)
neutraltraitsParam$s=c(0,0,1,1)

@@

tentries=replicate(10,modelOOstyle( N=N, Th=Th, K =K, m=m, b=b, r=r, rho=rho, d=d, maturity=maturity, endrepro=endrepro, logging="time", population=population,comus=initcomus, tstep=tstep, neutraltraitsParam=neutraltraitsParam))
